08-iris_comparison

### 2019-06-12 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
updated after meeting
adding journals back

@@

- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.

>>>>

### Statistical Paper Presenting Visual Diagnostic Tools for LIME

Write a paper that introduces some visual diagnostics for LIME to assess its performance. Key points that will be made:

1. explainer model is really bad (probably due to the binning)
2. local explanations at not local

@@

- Could try fitting a regression with interactions and see if LIME does a good job of explaining a model that is already interpretable.
- Run a simulation to understand if LIME is working
    - could implement a couple of local linear dependencies
    - piece this together
    - could include interactions in the model
    - does lime find the local models?
- Maybe we could come up with a test to compare between global and local explanations (but how would we do this?)

### 2019-06-12 journals/07-logistic_regression/07-logistic_regression.Rmd
adding journals back

```{r}
# Load libraries
library(furrr)
library(future)
library(gretchenalbrecht)
library(lime)
library(tidyverse)

@@

### Comparing the Two Models

@@

I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below. The results appear to be very different from the random forest results.

>>>>

```{r}
# Load libraries
library(furrr)
library(future)
library(glmnet)
library(gretchenalbrecht)
library(hierNet)
library(lime)
library(tidyverse)

@@

### LASSO Model

```{r}
# Fit or load the lasso logistic regression model
if(!file.exists("./data/logistic_lasso.rds")) {

  # Set a seed
  set.seed(20190312)

  # LASSO logistic regression model
  logistic_lasso <- cv.glmnet(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
                              y = hamby173and252_train %>% pull(samesource) %>% as.numeric(),
                              alpha = 1,
                              family = "binomial")

  # Tell R to run the upcoming code in parallel
  # plan(multiprocess)

  # LASSO logistic regression model with possible pairwise interactions
  # logistic_lasso <- 
  #   hierNet.logistic.path(x = hamby173and252_train %>% select(rf_features) %>% as.matrix(ncol = 9), 
  #                         y = hamby173and252_train %>% pull(samesource) %>% as.numeric(), 
  #                         lamlist = logistic_lasso$lambda)

  # Save the model
  saveRDS(logistic_lasso, "./data/logistic_lasso.rds")

  # Load the model
  logistic_lasso <- readRDS("./data/logistic_lasso.rds")

### Comparing the Models

@@

I also attempted to plot the features chosen by lime in order to visually assess the consistency. This plots are included below. The results appear to be different from the random forest results, but it is still possible to se vertical stripes that suggest a global interpretation as opposed to a local interpretation. However, the samesource bins do have some horizontal stipes that show what we would like to see. It is also interesting to note that the vertical bins are the most pronounced with the rfscore tree. This does not suprise me considering that these explanations are for a logistic regression and not the random forest model.

### 2019-06-12 journals/08-iris_comparison/08-iris_comparison.Rmd
compared to bullet
adding journals back

The following plots show the features chosen by each estimation method for all of the cases in the test dataset. The plots are created the by order the features are chosen (from first to third).

>>>>

The following plots show the features chosen by each estimation method for all of the cases in the test dataset. The plots are created the by order the features are chosen (from first to third). I am not seeing the same patterns that I saw with the bullet data and `rtrees`. Heike pointed out that you really do not need a complex model to explain this situation. The iris data should be easy to predict. Maybe I could switch to using the problem points in the iris data for the test data and see how LIME performs with these.
